% dvips -t letter lab_newton.dvi -o lab_newton.ps ; ps2pdf lab_newton.ps
\documentclass[11pt,titlepage,fleqn]{article}

\input{hw627_header}

\pagestyle{empty}

\newcommand{\vertgap}{\vspace{1cm}}

% change the figures to ``Figure L3'', etc
\renewcommand{\thefigure}{L\arabic{figure}}
\renewcommand{\thetable}{L\arabic{table}}
\renewcommand{\theequation}{L\arabic{equation}}
\renewcommand{\thesection}{L\arabic{section}}

%--------------------------------------------------------------
\begin{document}
%-------------------------------------------------------------

\begin{spacing}{1.2}
\centering
{\large \bf Lab Exercise: Iterative Newton method} \\
GEOS 626: Applied Seismology, Carl Tape \\
GEOS 627: Inverse Problems and Parameter Estimation, Carl Tape \\
%Assigned: February 9, 2012 --- Due: February 21, 2012
Last compiled: \today
\end{spacing}

%------------------------

\subsection*{Instructions}

Create a copy of the template program: \verb+cp lab_newton_template.m lab_newton.m+

\begin{enumerate}
\item Explain why the following three operations are equivalent: \verb+inv(6)*2+, \verb+6\2+, \verb+1/6*2+. \\
Type \verb+help \+

\item Open the template program \verb+lab_newton.m+.

What are \verb+F+, \verb+g+, and \verb+H+?

\vertgap

\item Using the Matlab built-in function \verb+fminbnd+, compute the (numerical) minimum of $F(\bem)$.

Plot the point $(\bem_{\rm min},\,F(\bem_{\rm min}))$ on the curve $F(\bem)$.

Zoom in to show that this appears to be a true minimum.

\item Implement the Newton algorithm (Tarantola, 2005, Eq. 6.291), and demonstrate (graphically or numerically) that you reach the minimum.

Plot the point $(\bem,\,F(\bem))$ for each new value of $\bem$.

Try several different starting values of $\bem$ to make sure it works.

\item Define a sensible stopping criterion.

\vertgap

\item Is your $F(\bem_{\rm min})$ lower or higher than Matlab's?

\vertgap

\item Repeat the experiment for a quadratic function. What happens?

\vertgap

\item For the quadratic function, solve for the analytical minimum, $\bem_{\rm min}$, and also $F(\bem_{\rm min})$.

\vertgap

\item Show mathematically that the Newton algorithm will give the solution.

\end{enumerate}

%-------------------------------------------------------------
%\bibliographystyle{agu08}
%\bibliography{car_abbrev,carl_main,carl_him}
%-------------------------------------------------------------

%-------------------------------------------------------------
\end{document}
%-------------------------------------------------------------
