% dvips -t letter lab_svd.dvi -o lab_svd.ps ; ps2pdf lab_svd.ps
\documentclass[11pt,titlepage,fleqn]{article}

\input{hw627_header}

\renewcommand{\baselinestretch}{1.1}

\newcommand{\vertgap}{\vspace{1cm}}

% change the figures to ``Figure L3'', etc
\renewcommand{\thefigure}{L\arabic{figure}}
\renewcommand{\thetable}{L\arabic{table}}
\renewcommand{\theequation}{L\arabic{equation}}
\renewcommand{\thesection}{L\arabic{section}}

%--------------------------------------------------------------
\begin{document}
%-------------------------------------------------------------

\begin{spacing}{1.2}
\centering
{\large \bf Lab Exercise: SVD approach to ballistic problem} \\
GEOS 627: Inverse Problems and Parameter Estimation, Carl Tape \\
Last compiled: \today
\end{spacing}

%------------------------

\subsection*{Overview}

This is Problem 3 from Chapter 3 \citep{AsterE2}, revisiting Example~1.1, which was featured in our second problem set (\verb+hw_ch1.pdf+). Review the Example~1.1 and the solutions to the problem (if needed). In this lab we apply SVD to the same problem. See Chapter 3 (and notes) for background on SVD.

%------------------------

\subsection*{Aster Chapter 3, Problem 3}

Using the parameter estimation problem described in Example~1.1 for determining the three parameters defining a ballistic trajectory, construct synthetic examples that demonstrate the following four cases using the SVD.

In each case, display and interpret the SVD components $\bU$, $\bV$, and $\bS$ in terms of the rank, $p$, of your forward problem $\bG$ matrix. Display and interpret any model and data null space vector(s) and calculate model and data space resolution matrices.
%
\begin{enumerate}
\item Three data points that are exactly fit by a unique model. \\
Plot your data points and the predicted data for your model.

\item Two data points that are exactly fit by an infinite suite of parabolas. \\
Plot your data points and the predicted data for a suite of these models.

\item Four data points that are only approximately fit by a parabola. \\
Plot your data points and the predicted data for the least squares model.

\item Two data points that are only approximately fit by any parabola, and for which there are an infinite number of least squares solutions. \\
Plot your data points and the predicted data for a suite of least squares models.
\end{enumerate}

%-------------------------------------------------------------
%\pagebreak
\bibliographystyle{agu08}
\bibliography{carl_abbrev,carl_main}
%-------------------------------------------------------------

%-------------------------------------------------------------
\end{document}
%-------------------------------------------------------------
