% dvips -t letter survey.dvi -o survey.ps ; ps2pdf survey.ps
% pdflatex survey
\documentclass[11pt,titlepage,fleqn]{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage[round]{natbib}
\usepackage{xspace}
\usepackage{epsfig}
\usepackage{bm}

%--------------------------------------------------------------
%       SPACING COMMANDS (Latex Companion, p. 52)
%--------------------------------------------------------------

\usepackage{setspace}    % double-space or single-space

\renewcommand{\baselinestretch}{1.0}

\textwidth 460pt
\textheight 690pt
\oddsidemargin 0pt
\evensidemargin 0pt

% see Latex Companion, p. 85
\voffset     -50pt
\topmargin     0pt
\headsep      20pt
\headheight   15pt
\headheight    0pt
\footskip     30pt
\hoffset       0pt

\include{carlcommands}

\graphicspath{
  {./figures/}
}

\pagestyle{empty}

%--------------------------------------------------------------
\begin{document}
%-------------------------------------------------------------

\noindent NAME: \line(1,0){150} \\
\noindent \today \\
\noindent GEOS 627, Inverse Problems and Parameter Estimation, Carl Tape
%\noindent GEOS 626, Applied Seismology, Carl Tape

\noindent
%{\bf Purpose}: I'd like to collect some basic information about each of you, in order to adapt the course materials.

\subsection*{Background information}

Please {\bf circle} your answer where options are provided.

\begin{enumerate}
\item What was (or is) your undergraduate degree? \line(1,0){150}

\item What degree are you pursuing? BS . MS . PhD

\noindent
What program (\eg solid-earth option of Geophysics)? \line(1,0){150}

\item What year are you? $\;\;$ U3 . U4 . G1 . G2 . G3 . G4 . G5 . G5+

The `G' refers to your years at UAF. If you have a previous master's degree, please list the field of study and thesis title here.

\noindent \line(1,0){400}

\item If you are a graduate student, what is your topic or your (projected) thesis title?

\noindent \line(1,0){400}

\noindent Who is your primary advisor? \noindent \line(1,0){150}

\item Previous courses. Please list any classes you have taken that covered
% 627
inverse problems or parameter estimation.
% 626
%seismology (or inverse problems).

\begin{tabular}{l|l|l}
\hline
course name & year taken & university \\ \hline\hline
calculus with vectors & & \hspace{3cm} \\ \hline
linear algebra & & \\ \hline
\hspace{8cm}  & & \\ \hline
 & & \\ \hline
% & & \\ \hline
\end{tabular}

\item What is your typical computing environment? desktop laptop

\item What is your typical computing platform? Mac Windows Linux

\item Have you used a linux/unix environment before? Y N

\item Status of your account on the UAF Seismology Linux Network:

\begin{enumerate}
\item I have an active account.
\item I have account but it may or may not be active.
\item I have no account; my preferred username is \line(1,0){100}
\end{enumerate}

\item Have you used ssh or some comparable remote log-in before? Y N

\item Describe your experience with computer programming, if any.

\vspace{0.5cm}


\item If there is a particular topic of
% 672
%inverse theory
% 626
seismology
that you'd like to see covered, feel free to list it here.
\end{enumerate}

%-------------------------------------------------------------
\end{document}
%-------------------------------------------------------------
