\begin{enumerate}
\item {\bf Attendance}: All students are expected to attend and participate in all classes and labs.

%\item {\bf Tardiness}: Students are expected to arrive in class prior to the start of each class. If a student does arrive late, they are expected to do so quietly and inform the instructor without disturbing the class.

\item {\bf Participation and preparation}: Students are expected to come to classes and labs with assigned reading and other assignments completed as noted in the syllabus.

\item {\bf Homework assignments}: 

\begin{enumerate}
\item All assignments are due {\bf at the start of class} on the due date. % noted in the Syllabus.
\item Late assignments will be accepted with a $10\%$ penalty per day late, up to five days late; an assignment that is $\ge 5$ days late will receive a zero. (An assignment that is ``one day late'' would be handed in less than 24 hours after the start time of class on the due date.)
%\item The lowest homework assignment will be dropped when computing the course grade.
\item No digital submission of assigments will be accepted. % (\eg email or Blackboard).
\item The contents within each assignment need to be correctly and clearly ordered and physically connected (\ie stapled, binder clip).
\end{enumerate}

{\bf Homework tips}: Please type or write neatly, keep the solutions in the order assigned and staple pages together. Include only relevant computer output in your solutions (a good approach is to cut and paste the relevant output for each problem into an editor such as Word or Latex). Clearly circle or highlight important numbers in the output, and label them with the question number.

I also suggest that you to include the most relevant portions of your code in your answers, especially in cases when you think your code is not working.  Display numerical answers with a reasonable number of significant figures and with {\em units} if the quantity is not dimensionless.

Homework scores are based on clarity of work, logical progression toward the solution, completeness of interpretation and summaries, and whether a correct solution was obtained.
%I encourage you to discuss homework problems with other students, however the work you turn in must be your own.

%\item {\bf Graded Assignments}: Assignments will be graded for students within seven days of their receipt and returned at the end of the next class.

\item {\bf Labs}: Computational labs are designed to provide technical training relevant for topics in the course and within the homework problems. Students are welcome to work in pairs on the lab exercises.

Labs will be graded on a scale from 0 to 2:
%
\begin{itemize}
\item[0] Student does not participate in lab and does not demonstrate completion of work.
\item[1] Student participates in lab but does not demonstrate completion of work.
\item[2] Student demonstrates completion of work.
\end{itemize}
%
``Completion of work'' will be identified by {\bf a subset of the lab questions}, not the entire lab.
{\em It is the student's responsibility to demonstrate completion of lab work.} This should be done during lab time or during office hour.

\item {\bf Reporting grades}: All student grades, transcripts, and tuition information are available on line at \verb+www.uaonline.alaska.edu+. %If you have difficulty accessing this website, contact the registrar at your local campus.

\item {\bf Consulting fellow students}: Students are permitted to discuss with each other general strategies for particular homework problems. However, the write-up that is handed in---including any computer codes---must be individual work.

\item {\bf Plagiarism:} Students must acknowledge any sources of information---including fellow students---that influenced their homework assignments or final project. Any occurrence of plagiarism will result in forfeiture of all points for the  particular homework assignment. If the plagiarism is between two students, then both students will potentially receive the penalty.

%Furthermore, the UAF catalog states: ``The university may initiate disciplinary action and impose disciplinary sanctions against any student or student organization found responsible for committing, attempting to commit or intentionally assisting in the commission of $\ldots$ cheating, plagiarism, or other forms of academic dishonesty\ldots''

\item All UA student academics and regulations are adhered to in this course. You may find these in the UAF catalog (section ``Academics and Regulations'').

\end{enumerate}
